\Notion{
    Summary
}{
    Function Structures: Domain, Range, Restriction, Extension.\\
    Function Operators: Equivalent, Inverse, Composition.\\
    Function Instances: Injective, Invertable, Compatible.\\
    Function Generalizations: Index System of Sets.\\
}

\Definition{
    Function
}{
    A binary relation $F$ is a function if and only if for every $a$ from $\domain{F}$ there is exactly one $b$ such that $a F b$.
    This unique $b$ is called the value of $F$ at $a$.
    $F(a)$ is not defined if $a$ $\not\in$ $domain{F}$.
}
\Note{
    A binary relation $F$ is called a \Keywords{function} (or \Keywords{mapping}, \Keywords{correspondence}) if \Keywords{$a F b_{1}$ and $a F b_{2}$ imply $b_{1}$ $=$ $b_{2}$} for any $a$, $b_{1}$, and $b_{2}$.
}
\Note{
    \Keywords{Function} is a \Keywords{procedure}, a \Keywords{rule}, \Keywords{assigning} to \Keywords{any object $a$ from the domain of the function} \Keywords{a unique object $b$, the value of the function at $a$}.
}
\Note{
    A \Keywords{function} represents \Keywords{a special type of relation}, a relation where every \Keywords{object $a$ from the domain} is \Keywords{related to} precisely \Keywords{one object in the range}, namely, to \Keywords{the value of the function at $a$}.
}

\Proposition{}{
    Let $F$ and $G$ be functions.
    \Keywords{$F$ $=$ $G$} if and only if \Keywords{$\domain{F}$ $=$ $\domain{G}$ and $F(x)$ $=$ $G(x)$} for all $x$  $\in$ $\domain{F}$.
}{
    The Axiom of Extensionality.
}

\Definition{}{
    Let $F$ be a function and $A$ and $B$ sets.
    \List{enumerate}{
        \item{
            $F$ is a function on $A$ if $\domain{F}$ $=$ $A$.
        }
        \item{
            $F$ is a function into $B$ if $\range{F}$ $\subseteq$ $B$.
        }
        \item{
            $F$ is a function onto $B$ if $\range{F}$ $=$ $B$.
        }
        \item{
            The restriction of the function $F$ to $A$ is the function $F \restriction A$ $=$ $\SetComprehension{(a,b) \in F}{a \in A}$.
        }
        \item{
            If $G$ is a restriction of $F$ to some $A$, we say that $F$ is an extension of $G$.
        }
    }
}
\Note{
    Concepts of domain, range, image, inverse image, inverse, and composition can be applied to functions.
}

\Proposition{}{
    Let $f$ and $g$ be functions.
    Then \Keywords{$g {\composition} f$ is a function}, \Keywords{$g {\composition} f$ is defined at $x$} if and only if \Keywords{$f$ is defined at $x$ and $g$ is defined at $f(x)$}.
    \List{enumerate}{
        \item{
            \Keywords{$\domain{(g {\composition} f)}$ $=$ $\domain{f} \cap  \Inverse{f}[\domain{g}]$}.
        }
        \item{
            \Keywords{$(g {\composition} f)(x)$ $=$ $g(f(x))$} for all $x$ $\in$ $\domain(g {\composition} f)$.
        }
    }
}{
    Obviously.
}

\Definition{
    Invertiable
}{
    A function $f$ is invertible if $\Inverse{f}$ is a function.
}
\Proposition{}{
    If $f$ is a function, its \Keywords{inverse $\Inverse{f}$ is a relation}, but it \Keywords{may not be a function}.
}{
    Obviously.
}

\Definition{}{
    A function $f$ is called one-to-one or injective if $a_{1}$ $\in$ $\domain{f}$, $a_{2}$ $\in$ $\domain{f}$, and $a_{1}$ $\neq$ $a_{2}$ implies $f(a_{1})$ $\neq$ $f(a_{2})$.
    In other words if $a_{1}$ $\in$ $\domain{f}$, $a_{2}$ $\in$ $\domain{f}$, and $f(a_{1})$ $=$ $f(a_{2})$ implies $a_{1}$ $=$ $a_{2}$·
}
\Note{
    A one-to-one function attains different values for different elements from its domain.
}
\Proposition{}{
    A function is \Keywords{invertible} if and only if it is \Keywords{one-to-one}.
}{
    Let $f$ be invertible; then $\Inverse{f}$ is a function.
}
\Proposition{}{
    If \Keywords{$f$ is invertible}, then \Keywords{$\Inverse{f}$ is also invertible}.
}{
    $\Inverse{(\Inverse{f})}$ $=$ $f$.
}

\Definition{}{
    Function $f$ and $g$ are called compatible if $f(x)$ $=$ $g(x)$ for all $x$ $\in$ $\domain{f} \cap \domain{g}$.
}
\Definition{}{
    A set of functions $F$ is called a compatible system of functions if any two functions $f$ and $g$ from $F$ are compatible.
}
\Proposition{}{
    Functions \Keywords{$f$ and $g$ are compatible} if and only if \Keywords{$f \cup g$ is a function}.
    Functions \Keywords{$f$ and $g$ are compatible} if and only if \Keywords{$f \restriction (\domain{f} \cap \domain{g})$ $=$ $g \restriction (\domain{f} \cap \domain{g})$}.
}{
    Obviously.
}

\Theorem{}{
    If $F$ is a \Keywords{compatible system of functions}, the $\bigcup F$ is a \Keywords{function} with \Keywords{$\domain(\bigcup F)$ $=$ $\bigcup\SetComprehension{\domain{f}}{f \in F}$}.
    The function $\bigcup F$ \Keywords{extends all $f \in F$}.
}{
    Obviously.
}

\Definition{}{
    Let $A$ and $B$ be sets.
    The set of all functions on $A$ into $B$ is denoted $B^{A}$. 
}
\Proposition{}{
    \Keywords{$B^{A}$ exists}.
}{
    $B^{A}$ $\subseteq$ $\Powerset{A \cartesianproduct B}$.
}

\Definition{
    Indexed System of Sets
}{
    Let $S$ $=$ $\FunctionComprehension{S_{i}}{i \in I}$ be a function with domain $I$, the values $S_{i}$ are arbitrary sets.
    We call the function $\FunctionComprehension{S_{i}}{i \in I}$ an indexed system of sets, whenever we wish to stress that the values of $S$ are sets.
}
\Definition{
    be Indexed by
}{
    $A$ $=$ $\SetComprehension{S_{i}}{i \in I}$ $=$ $\range{S}$, where $S$ is a function on $I$.
}
\Proposition{}{
    $\bigcup{A}$ and $\bigcap{A}$ were defined for any system of sets $A$($A$ $\neq$ $\emptyset$ in case of intersection).
    $\bigcup{A}$ $=$ $\bigcup{\SetComprehension{S_{i}}{i \in I}}$ $=$ $\underset{i \in I}{\bigcup}S_{i}$;
    $\bigcap{A}$ $=$ $\bigcap{\SetComprehension{S_{i}}{i \in I}}$ $=$ $\underset{i \in I}{\bigcap}S_{i}$.
}{
    Obviously.
}
\Property{}{
    Every system of sets $A$ can be indexed by a function.
}{
    Obviously.
}

\Definition{
    Product of the Indexed System
}{
    Let $S$ $=$ $\FunctionComprehension{S_{i}}{i \in I}$ and $f$ be a function on $I$.
    $\prod S$ $=$ $\SetComprehension{f}{\QuantifierCondition{\forall}{i \in I}{f_{i} \in S_{i}}}$
}
\Proposition{}{
    \Keywords{$\prod_{i \in I} S_i$ exists}.
}{
    $\prod_{i \in I} S_{i}$ $\subseteq$ $\Powerset{(I \cartesianproduct \bigcup_{i \in I} S_{i})}$
}

\Definition{
    Exponentiation of Sets
}{
    If the indexed system $S$ is such that $S_{i} = B$ for all $i \in I$, then $\prod_{i \in I} S_{i}$ $=$ $B^{I}$
}
\Note{
    The "exponentiation" of sets is related to "multiplication" of sets in the same way as similar operations on numbers are related.
}
