\Definition{
	Subset,
	included in
}{
	$A$ is a subset of (included in) $B$ if, for every $x$, $x \in A$ implies $x \in B$ and denoted by $A \subseteq B$.
}
\Property{}{
	$A \subseteq B \land B \subseteq C \implies A \subseteq C$.
}{
	Obviously.
}
\Definition{
	Inclusion
}{
	The property $\subseteq$.
}
\Theorem{}{
	$A \subseteq A$.\newline
	If $A \subseteq B$ and $B \subseteq A$, then $A = B$.\newline
	If $A \subseteq B$ and $B \subseteq C$, then $A \subseteq C$.
}{
	Obviously.
}
\Definition{
	Proper Subset,
	properly contained in
}{
	If $A \subseteq B$ and $A \neq B$, $A$ is a proper subset of $B$ ($A$ is properly contained in $B$) and denoted by $A \subset B$.
}
\Definition{
	Intersection
}{
	The intersection of $A$ and $B$, $A \cap B$, is the set of all $x$ which belong to both $A$ and $B$.
    The intersection $\bigcap S$ of a nonempty system of sets $S$: $x \in \bigcap S$ if and only if $x \in A$ for all $A \in S$.
}
\Property{}{
    $\bigcap \emptyset$ would have to be a set of all sets.
}{
    Every $x$ belongs to all $ \in \emptyset$.
}
\Theorem{}{
	$\cap emptyset$ would have to be a set of all sets.
}{
	Obviously.
}
\Definition{
	Disjoint
}{
	$A$ and $B$ are disjoint if $A \cap B = emptyset$.
}
\Definition{
	Mutually Disjoint
}{
	$S$ is a system of mutually disjoint sets if $A \cap B = emptyset$ for all $A, B \in S$ such that $A \neq B$.
}
\Definition{
	Union
}{
	The union of $A$ and $B$, $A \cup B$, is the set of all $x$ which belong in either $A$ or $B$ (or both).
}
\Definition{
	Difference
}{
	The difference of $A$ and $B$, $A - B$, is the set of all $x \in A$ which do not belong to $B$.
}
\Definition{
	Symmetric Difference
}{
	The symmetric difference of $A$ and $B$, $A \triangle B$, is defined by $A \triangle B = (A-B) \cup (B-A)$.
}
\Property{
	Commutativity
}{
	$A \cap B = B \cap A$,
	$A \cup B = B \cup A$,
    $A \triangle B = B \triangle A$
}{
	Obviously
}
\Property{
	Associativity
}{
	$(A \cap B) \cap C = A \cap (B \cap C)$,
	$(A \cup B) \cup C = A \cup (B \cup C)$,
    $(A \triangle B) \triangle C = A \triangle (B \triangle C)$,
}{
	Obviously
}
\Note{
	We do not need parentheses for the intersection, union and for more than three sets.
}
\Property{
	Distributivity
}{
	$A \cap (B \cup C) = (A \cap B) \cup (A \cap C)$,
	$A \cup (B \cap C) = (A \cup B) \cap (A \cup C)$
}{
	Obviously
}
\Property{
	DeMorganlaws
}{
	$C - (A \cap B) = (C - A) \cup (C - B)$,
	$C - (A \cup B) = (C - A) \cap (C - B)$
}{
	Obviously
}
\Property{}{
	$A - B = \emptyset$ if and only if $A \subseteq B$.
}{
	Obviously.
}
\Property{}{
    $A \triangle A = \emptyset$
}{
    Obviously.
}