\Definition{
    Unordered Pair
}{
    \Set{$a, b$} is a set whose elements are exactly $a$ and $b$.
}
\Definition{
    Ordered Pair
}{
    Ordered pair of $a$ and $b$ is denoted by $(a, b)$.
}
\Definition{
    Coordinate
}{
    $a$ is the first coordinate of the pair, $b$ is the second coordinate.
}
\Definition{}{
    $(a, b)$ $=$ \Set{\Set{$a$}, \Set{$a, b$}}.
}
\Definition{}{
    For two different sets $\alpha$ and $\beta$, $(a, b)$ $=$ \Set{\Set{$a, \alpha$}, \Set{$b, \beta$}}.
}
\Note{
    An alternative definition of ordered pairs.
}

\Property{}{
    Two ordered pairs are equal if and only if their first coordinates are equal and their second coordinates are equal.
}{
    Obviously.
}
\Property{}{
    $(a, b)$ $\neq$ $(b, a)$ if $a$ $\neq$ $b$.
}{
    Obviously.
}
\Property{}{
    If $a$ $\neq$ $b$, $(a, b)$ has two elements, a singleton $\Set{a}$ and an unordered pair $\Set{a, b}$.
    If $a$ $=$ $b$, then $(a, a)$ $=$ $\Set{\Set{a}}$ has only one element.
}{
    Obviously.
}
\Note{
    We find the first coordinate by looking at the element of $\Set{a}$.
    The second coordinate is then the other element of $\Set{a, b}$.
}
\Note{
    Ordered pair should be defined in such a way that two ordered pairs are equal if and only if their first coordinates are equal and their second coordinates are equal.
}
\Note{
    If $a \neq b$, $(a, b)$ has two elements, a singleton $\Set{a}$ and an unordered pair $\Set{a, b}$.
    The first coordinate is the element of $\Set{a}$; the second coordinate is the other element of $\Set{a, b}$.
}
\Theorem{}{
    $(a, b)$ $=$ $(a', b')$ if and only if $a$ $=$ $a'$ and $b$ $=$ $b'$.
}{
    Obviously.
}

\Definition{
    One-Tuples
}{
    $(a)$ $=$ $a$.
}
\Definition{
    Ordered Triples
}{
    $(a, b, c)$ $=$ $((a, b), c)$.
}
\Definition{
    Ordered Quadruples
}{
    $(a, b, c, d)$ $=$ $(((a, b), c), d)$.
}

\Property{}{
    $(a, b)$ $\in$ \Powerset{\Powerset{\Set{$a, b$}}}.
    More generally, if $a$ $\in$ $A$ and $b$ $\in$ $A$, then $(a, b)$ $\in$ \Powerset{\Powerset{\Set{$a, b$}}}.
}{
    Obviously.
}
\Property{}{
    $a$, $b$ $\in$ $\bigcup(a, b)$.
}{
    Obviously.
}
\Property{}{
    $(a, b)$, $(a, b, c)$, and $(a, b, c, d)$ exist for all $a$, $b$, $c$, and $d$.
}{
    Obviously.
}
\Property{}{
    If $(a, b)$ $=$ $(b, a)$, then $a$ $=$ $b$.
}{
    Obviously.
}
\Property{}{
    $(a, b, c)$ $=$ $(a', b' ,c')$ implies $a$ $=$ $a'$, $b$ $=$ $b'$, and $c$ $=$ $c'$.
    $(a, b, c, d)$ $=$ $(a', b' ,c', d')$ implies $a$ $=$ $a'$, $b$ $=$ $b'$, $c$ $=$ $c'$, and $d$ $=$ $d'$.
}{
    Obviously.
}

